---
title: "Exercise to make plots with one or two variables"
author: "Christopher Rohde"
date: "17/6/2021"
output: html_document
---



# 1a. Distribution of age
ggplot(___, aes(x = ___)) +
    ___()
    
# 1b. Distribution of age of diabetes diagnosis
ggplot(___, aes(x = ___)) +
    ___()

# 2a. Number of people who smoke now
ggplot(___, aes(x = ___)) +
    ___()

# 2b. Number of people who are physically active
ggplot(___, aes(x = ___)) +
    ___()

# 3a. BMI in relation to systolic blood pressure
ggplot(___, aes(x = ___, y = ___)) +
    ___()

# 3b. BMI relation to diastolic blood pressure
ggplot(___, aes(x = ___, y = ___)) +
    ___()
    
# 4. Physically active people with or without diabetes
ggplot(___, aes(x = ___, fill = ___)) +
    ___(___ = ___())

# 5. Poverty levels between those with or without diabetes
ggplot(___, aes(x = ___, y = ___)) +
    ___()

# OPGAVE 11.5.1
```{r}
ggplot(nhanes_small, aes(x = age)) +
    geom_histogram()
    
ggplot(nhanes_small, aes(x = diabetes_age)) +
    geom_histogram()

```

# opgave 11.5.2
```{r}
ggplot(nhanes_small, aes(x = smoke_now)) +
    geom_bar()

ggplot(nhanes_small, aes(x = phys_active)) +
    geom_bar()
```

# opgave 11.5.3

```{r}
ggplot(nhanes_small, aes(x = bp_sys_ave, y = bmi)) +
    geom_hex()

ggplot(nhanes_small, aes(x = bp_dia_ave, y = bmi)) +
    geom_hex()
```

# opgave 11.5.4

```{r}
ggplot(nhanes_small, aes(x = diabetes, fill = phys_active)) +
    geom_bar(position = position_dodge())
```

# opgave 11.5.5

```{r}
ggplot(nhanes_small, aes(x = diabetes, y = poverty)) +
    geom_violin()

nhanes_small %>% 
    drop_na(diabetes) %>% 
    ggplot(aes(x = diabetes, y = poverty)) +
    geom_violin()
```

